\vspace*{-8mm}\textbf{\textsc{Novelty Detection for Semantic Place Categorization}}

### 2011-06-26 thesis/novelty-intro.tex
Some changes in the novelty section.

\subsection{Assumption on a constant $P(novel)$}
The ratio between the conditional and unconditional probabilities of the sensed variables
is only directly applicable to novelty detection under the assumption of a constant $P(novel)$.

All the literature focus on novelty detection within a fixed scenario, where the set of variables
used to model the distribution is fixed and defined at the moment the threshold is trained.
Due to that, they can drop a constant $P(novel)$ and never need to directly or indirectly calculate
it.
To the best of the author knowledge there has not been studies on how to approximate it on dynamic
sets and structures of sensed variables, and so a strong assumption on being constant through all
the possible scenarios is used to allow dropping the factor.

This assumption was considered questionable on whether it holds on a realistic scenario,
and for that a sampling scheme able to comply with it is now presented as well an unbiased sampling
scheme. A method to generate samples that match this \emph{criterium} of having a constant $P(novel)$ can be:

>>>>

\subsection{Assumption about Constant $P(novel)$}
The ratio between the conditional and unconditional probabilities of the sensed variables
is only directly applicable to novelty detection under the assumption of a constant $P(novel)$.

All the literature focuses on novelty detection within a fixed scenario, where the set of variables
used to model the distribution is fixed and defined at the moment the threshold is trained.
Due to that, it is possible to drop the constant $P(novel)$ and there is no need to calculate
it directly or indirectly.
To the best of the knowledge of the author there has been no studies on how to approximate it on dynamic
sets and structures of sensed variables and a strong assumption has always been used about the factor being 
constant through all possible scenarios.

It is questionable whether this assumption holds in realistic scenarios.
\textbf{[Read the section from here on.]}
and for that a sampling scheme able to comply with it is now presented as well an unbiased sampling
scheme. A method to generate samples that match this \emph{criterium} of having a constant $P(novel)$ can be:
